\chapter*{Conclusion} 
\addcontentsline{toc}{chapter}{Conclusion} % Adds to Table of Contents
\lhead{\emph{Conclusion}}

In conclusion, the \textbf{ft\_transcendence} project successfully achieved its objective of developing a modern, full-stack web application centered around the classic game of Pong. It delivers a feature-rich Single Page Application (SPA) providing multiple gameplay modes, including 1 vs 1 online matches, contests against an AI opponent, local 4-player games, and structured tournaments. Key features enhancing user engagement include user profiles with avatars, match history, and a friends system.

The project demonstrates proficiency across a range of modern web technologies and practices. The backend, built with Django and Django Rest Framework, provides a secure RESTful API. User authentication is robust, offering native credentials, 42 OAuth integration, JWT-based session management via secure cookies, and optional TOTP 2FA. The frontend utilizes vanilla JavaScript and the HTML5 Canvas for dynamic game rendering, ensuring a responsive experience without reliance on large frameworks. Data persistence is handled innovatively through PostgreSQL for primary application data and an Ethereum sidechain for immutable tournament record-keeping, interacted with via Web3.py. The entire application is containerized using Docker and orchestrated with Docker Compose, including Nginx for web serving/reverse proxying and the ELK stack for centralized logging and monitoring, showcasing production-grade DevOps practices.

Adherence to the Software Development Life Cycle (SDLC), including requirements definition, architectural design, implementation, and multi-faceted testing (unit, integration, manual E2E, security, usability), ensured a systematic approach to development and quality assurance. The project successfully addressed technical challenges related to real-time interactions, security implementation, and cross-component integration within a containerized environment.

Future work could focus on areas identified during evaluation, such as implementing comprehensive automated End-to-End testing, conducting more extensive performance and load testing, potentially adding a real-time chat feature, and further refining the AI opponent's capabilities. This project serves as a strong demonstration of integrating diverse technologies to build a secure, scalable, and engaging web-based gaming platform.
