\addcontentsline{toc}{section}{References}

\begin{thebibliography}{99}

\bibitem{intra-api}
42 (n.d.). Intra API documentation. Retrieved October 20, 2024, from \url{https://api.intra.42.fr/apidoc/guides/}

\bibitem{battistin2022}
Battistin, T., Dalla Pozza, N., Trentin, S., Volpin, G., Franceschini, A., \& Rodà, A. (2022). Co-designed mini-games for children with visual impairment: A pilot study on their usability. \textit{Multimedia Tools and Applications}. \url{https://doi.org/10.1007/s11042-022-13665-7}

\bibitem{bootstrap}
Bootstrap. (n.d.). Bootstrap documentation. Retrieved September 15, 2024, from \url{https://getbootstrap.com/docs}

\bibitem{django}
Django Software Foundation. (n.d.). Django documentation (version 5.0). Retrieved September 15, 2024, from \url{https://docs.djangoproject.com/en/5.0/}

\bibitem{django-otp}
Django OTP contributors. (n.d.). Django OTP documentation. Retrieved October 28, 2024, from \url{https://django-otp-official.readthedocs.io/en/latest/}

\bibitem{drf}
Encode OSS Ltd. (n.d.). Django REST framework documentation. Retrieved October 28, 2024, from \url{https://www.django-rest-framework.org/}

\bibitem{docker}
Docker Inc. (n.d.). Docker documentation. Retrieved October 28, 2024, from \url{https://docs.docker.com/}

\bibitem{ecma}
Ecma International. (n.d.). ECMAScript language specification. Retrieved September 25, 2024, from \url{https://www.ecma-international.org/publications-and-standards/}

\bibitem{elastic}
Elastic. (n.d.). Elastic Stack and Product Documentation. Retrieved October 28, 2024, from \url{https://www.elastic.co/guide/index.html}

\bibitem{geeksforgeeks}
GeeksforGeeks. (2024). What is single page application? Available at: \url{https://www.geeksforgeeks.org/what-is-single-page-application/}

\bibitem{guanabara_js}
Guanabara, G. (2019). Curso de JavaScript [Video]. YouTube. \url{https://www.youtube.com/watch?v=1-w1RfGIov4}

\bibitem{guanabara_html_css}
Guanabara, G. (2020). Curso de HTML e CSS [Video]. YouTube. \url{https://www.youtube.com/watch?v=1-w1RfGIov4}

\bibitem{mosh}
Programming with Mosh. (2021). Python Django tutorial for beginners [Video]. YouTube. \url{https://www.youtube.com/watch?v=rHux0gMZ3Eg}

\bibitem{nginx}
Nginx Inc. (n.d.). Nginx documentation. Retrieved October 28, 2024, from \url{https://nginx.org/en/docs/}

\bibitem{postgresql}
The PostgreSQL Global Development Group. (n.d.). PostgreSQL documentation. Retrieved October 26, 2024, from \url{https://www.postgresql.org/docs/current/}

\bibitem{simple_jwt}
Simple JWT. (n.d.). Simple JWT documentation. Retrieved October 18, 2024, from \url{https://django-rest-framework-simplejwt.readthedocs.io/en/latest/}

\bibitem{solidity}
Ethereum Foundation. (n.d.). Solidity documentation. Retrieved October 28, 2024, from \url{https://docs.soliditylang.org/}

\bibitem{stakeholdermap}
Stakeholdermap.com. (n.d.). Risk assessment matrix - Simple 3x3. Retrieved October 26, 2024, from \url{https://www.stakeholdermap.com/risk/risk-assessment-matrix-simple-3x3.html}

\bibitem{web3py}
Web3.py contributors. (n.d.). Web3.py documentation. Retrieved October 28, 2024, from \url{https://web3py.readthedocs.io/en/stable/}

\bibitem{wikipedia}
Wikipedia contributors. (n.d.). Single-page application. Wikipedia, The Free Encyclopedia. Retrieved September 8, 2024, from \url{https://en.wikipedia.org/wiki/Single-page_application}

\end{thebibliography}
