%% ----------------------------------------------------------------
%% Thesis.tex -- MAIN FILE (the one that you compile with LaTeX)
%% ---------------------------------------------------------------- 

% Set up the document
\documentclass[a4paper, 11pt, oneside]{Thesis}  % Use the "Thesis" style, based on the ECS Thesis style by Steve Gunn
\usepackage[titletoc]{appendix}% https://ctan.org/pkg/appendix

\graphicspath{{Figures/}}  % Location of the graphics files (set up for graphics to be in PDF format)

% Include any extra LaTeX packages required
\usepackage[square, numbers, comma, sort&compress]{natbib}  % Use the "Natbib" style for the references in the Bibliography
%\usepackage{natbib}
\usepackage{verbatim}  % Needed for the "comment" environment to make LaTeX comments
\usepackage{vector}  % Allows "\bvec{}" and "\buvec{}" for "blackboard" style bold vectors in maths
\usepackage{placeins}

\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{pdflscape} % Added for landscape orientation of figures
\usepackage{rotating} % Added for rotated text in tables
\usepackage{multicol} % Added for multi-column layouts
\usepackage{enumitem} % Added for enhanced list environments
\hypersetup{urlcolor=blue, colorlinks=true}  % Colours hyperlinks in blue, but this can be distracting if there are many links.
\renewcommand{\bibname}{References}

%% ----------------------------------------------------------------
\begin{document}
\frontmatter	  % Begin Roman style (i, ii, iii, iv...) page numbering

% Set up the Title Page
\title  {ft\_transcendence}
 
\authors  {\texorpdfstring
            {\href{your web site or email address}{enrico@42abudhabi.ae}}
            { }
            }
\addresses  {\groupname\\\deptname\\\univname}  % Do not change this here, instead these must be set in the "Thesis.cls" file, please look through it instead
\date       {\today}
\subject    {}
\keywords   {}

\maketitle
%% ----------------------------------------------------------------

\setstretch{1.3}  % It is better to have smaller font and larger line spacing than the other way round

% Define custom page styles for chapter pages and regular pages
\fancypagestyle{chapterfirst}{%
  \fancyhf{} % Clear all headers and footers
  \fancyfoot[C]{\thepage} % Page number at bottom center
  \renewcommand{\headrulewidth}{0pt} % No header rule
}

\fancypagestyle{chapterrest}{%
  \fancyhf{} % Clear all headers and footers
  \fancyhead[L]{\leftmark} % Chapter number and title at top left
  \fancyhead[R]{\thepage} % Page number at top right
  \renewcommand{\headrulewidth}{0.4pt} % Header rule
}

% Format for chapter headers - important to define this before modifying the chapter command
\renewcommand{\chaptermark}[1]{\markboth{\chaptername\ \thechapter.\ #1}{}} 

% Modify chapter command to use chapterfirst style on first page
\makeatletter
\let\stdchapter\chapter
\renewcommand*{\chapter}{%
  \cleardoublepage % Start each chapter on a new page
  \thispagestyle{chapterfirst}% First page of chapter uses firstpage style
  \stdchapter
}
\makeatother

% Set the default pagestyle to chapterrest
\pagestyle{chapterrest}

%% ----------------------------------------------------------------
% Declaration Page required for the Thesis, your institution may give you a different text to place here
\clearpage  % Declaration ended, now start a new page
% The Abstract Page
\addtotoc{Abstract}  % Add the "Abstract" page entry to the Contents
\abstract{ 
\addtocontents{toc} {\vspace{1em}} % Add a gap in the Contents, for aesthetics

The growing challenge of creating secure, interactive web-based gaming applications has led to new approaches combining traditional web frameworks with blockchain technology and modern DevOps practices. Web-based gaming applications face significant challenges in delivering seamless multiplayer experiences while maintaining security, performance, and data integrity. The classic Pong game provides an ideal foundation to explore these challenges, raising the question of how modern web technologies can be leveraged to create a feature-rich, secure, and scalable gaming platform. ft\_transcendence is a modern, feature-rich clone of the classic Pong game implemented as a full-stack web application that addresses these challenges. Prior implementations of web-based Pong games have often lacked integration with modern security practices, blockchain technology, and containerized deployment strategies. Many existing solutions fail to address the security vulnerabilities inherent in web applications, particularly when running containerized services as root users. This project demonstrates the integration of real-time gameplay, secure authentication, on-chain tournament recording, and full DevOps automation within a Docker-Compose stack. The backend is powered by Django and PostgreSQL, exposing a clean RESTful API secured with JWT cookies and optional TOTP-based Two-Factor Authentication (2FA). Users can authenticate via 42 OAuth or traditional credentials with proper security measures including non-root container execution. The frontend, crafted using vanilla JavaScript and Bootstrap 5, delivers a responsive single-page application rendered on an HTML5 <canvas> element for immersive gameplay. Game modes include 1v1, AI opponents, 4-player multiplayer, and tournament brackets. Match and tournament data are stored both in PostgreSQL and on an Ethereum sidechain, ensuring immutability and verifiability. Static content and reverse proxying are handled by Nginx, which also enforces HTTPS using TLS. The system integrates centralized logging and monitoring through the ELK stack, and supports production-grade deployment via Docker and Makefiles. The implementation achieves cross-browser compatibility and accessibility for visually impaired users. This research demonstrates how combining traditional web technologies with blockchain solutions creates secure, verifiable gaming experiences while addressing critical security vulnerabilities through proper container user management. The architecture showcases a framework for building scalable web applications that maintain data integrity while enhancing user engagement through profile customization, friends lists, online status, and detailed match history.
}



\clearpage  % Abstract ended, start a new page
%% ----------------------------------------------------------------
\clearpage  % End of the Acknowledgements
%% ----------------------------------------------------------------

\pagestyle{chapterrest}  % Use our custom page style consistently throughout the document


%% ----------------------------------------------------------------
% Define frontmatter page style
\fancypagestyle{frontmatter}{%
  \fancyhf{} % Clear all headers and footers
  \fancyhead[L]{\emph{\leftmark}} % Set the left side page header
  \fancyhead[R]{\thepage} % Page number at top right
  \renewcommand{\headrulewidth}{0.4pt} % Header rule
}

% Table of Contents
\cleardoublepage % Start on a new page
\markboth{Contents}{} % Set the left mark for this section
\pagestyle{frontmatter} % Use the frontmatter style
\tableofcontents  % Write out the Table of Contents

%% ----------------------------------------------------------------
% List of Figures
\cleardoublepage % Start on a new page
\markboth{List of Figures}{} % Set the left mark for this section
\listoffigures  % Write out the List of Figures

%% ----------------------------------------------------------------
% List of Tables
\cleardoublepage % Start on a new page
\markboth{List of Tables}{} % Set the left mark for this section
\listoftables  % Write out the List of Tables

%% ----------------------------------------------------------------
% List of Abbreviations
\cleardoublepage % Start on a new page
\markboth{List of Abbreviations}{} % Set the left mark for this section
\chapter*{List of Abbreviations}  % Create a new unnumbered chapter for the abbreviations
\addcontentsline{toc}{chapter}{List of Abbreviations}  % Add this to the Table of Contents

% Use a more compact format with reduced spacing to fit on one page
\vspace{-5mm}
\begin{description}[leftmargin=3cm,labelwidth=2.5cm,itemsep=1pt,font=\normalfont]
\item[\textbf{2FA}] Two-Factor Authentication
\item[\textbf{CI/CD}] Continuous Integration and Continuous Delivery/Deployment
\item[\textbf{DOM}] Document Object Model
\item[\textbf{DevOps}] Development Operations
\item[\textbf{Git}] Global Information Tracker
\item[\textbf{JWT}] JSON Web Tokens
\item[\textbf{OAuth}] Open Authorization
\item[\textbf{OTP}] One-Time Password
\item[\textbf{SPA}] Single Page Application
\item[\textbf{SDLC}] Software Development Life Cycle
\item[\textbf{SSR}] Server-Side Rendering
\item[\textbf{SQL}] Structured Query Language
\item[\textbf{TLS}] Transport Layer Security
\item[\textbf{UI}] User Interface
\item[\textbf{URL}] Uniform Resource Locator
\item[\textbf{XSS}] Cross-Site Scripting
\end{description}

%% ----------------------------------------------------------------
% Reset the header for the main content
\cleardoublepage % Start main content on a new page
\pagestyle{chapterrest} % Use our custom page style
\renewcommand{\sectionmark}[1]{\markright{\thesection\ #1}} % Format for section headers



\setstretch{1.3}  % Return the line spacing back to 1.3



%% ----------------------------------------------------------------
\mainmatter	  % Begin normal, numeric (1,2,3...) page numbering
\pagestyle{chapterrest}  % Use our custom page style for chapter pages

% Include the chapters of the thesis, as separate files
% Just uncomment the lines as you write the chapters

\input{./Chapters/Chapter1}

\input{./Chapters/Chapter2}

\input{./Chapters/Chapter3}

\input{./Chapters/Chapter4}

\input{./Chapters/Chapter5}

\input{./Chapters/Chapter6}

\input{./Chapters/Chapter7}

\input{./Chapters/Chapter8}

%% ----------------------------------------------------------------

%% ----------------------------------------------------------------
%% ----------------------------------------------------------------
% Now begin the Appendices, including them as separate files

\addtocontents{toc}{\vspace{2em}}  % Add a gap in the Contents, for aesthetics
% Now begin the Appendices, including them as separate files

\input{./conclusion}


\input{./appendix}

\input{./references}

% that's all folks :)

\end{document}  % The End
%% ----------------------------------------------------------------